---
title: "Coursera Assignment-PML"
author: "Helen-R"
date: "Monday, October 25, 2014"
output:
  html_document: default
---
## A. Load the dataset:
```{r LoadDataset, cache=TRUE}
library(caret); library(randomForest); library(rattle); library(doSNOW);
registerDoSNOW(makeCluster(2, type = "SOCK"))
setwd("D:/Data Analysis/R/ML/Pj-dumbell")

url_tr <- "D:/Data Analysis/R/ML/Pj-dumbell/pml-training.csv"
url_te <- "D:/Data Analysis/R/ML/Pj-dumbell/pml-testing.csv"
tr <- read.csv(url_tr, fileEncoding = 'UTF-8')
te <- read.csv(url_te, fileEncoding = 'UTF-8')
```
The dumbbell lifting quality test is performed by 6 male participants between 20-28 year-old. [ref.1][01]    
There are:    
- `r dim(tr)[2]` variables (= features, predictors, characteristics),    
- `r dim(tr)[1]` observations in the training set,    
- `r dim(te)[1]` sets for testing.    
    
### Tidy the dataset
Among `r dim(tr)[2]` variables:    
Variables 1~7 indicate the participants, time stamps, and activities (window, num).    
```{r var1to7, echo=FALSE, cache=TRUE}
names(tr)[1:7]
```
### Omit NAs and blanks: 52 features left, and column "classe"" is the outcome
**Subsetting the data:** ignore columns of NA and blank, and column X.    
1. locations: belt/arm/forearm/dumbbell    
2. Each location has 13 variables:     
- 3 variables from roll/pitch/yaw (Euler angle)     
- 3 variables from [gyro] x/y/z       
- 4 variables from [accel] x/y/z/total        
- 3 variables from [magnet] x/y/z     
```{r var_analysis, cache=TRUE}
train_raw <- tr[, c(2:11, 37:49, 60:68, 84:86, 102, 113:124, 140, 151:160)]
test_raw <- te[, c(2:11, 37:49, 60:68, 84:86, 102, 113:124, 140, 151:160)]
```
**Data slicing**    
Training vs. cross-validation is **"60:40"**    
```{r features, cache=TRUE}
set.seed(151)
inTrain <- createDataPartition(y=train_raw$classe, p = 0.6, list=F)
tr_set <- train_raw[inTrain,]
tr_cv <- train_raw[-inTrain,]
```
## B. Data training & cross-validation    
```{r train, cache=TRUE}
set.seed(234)
rFraw <- randomForest(tr_set[,7:58], y = tr_set$classe, xtest=tr_cv[,7:58], ytest=tr_cv$classe, ntree=1000, keep.forest=T)
```
### Show confusion matrix and error rate    
```{r confMx, echo=FALSE, cache=TRUE}
rFraw
plot(rFraw)
```
                        
## C. Predicting    
### According to the above random forest, the prediction to the test set is as follow:    
```{r prediction, cache=TRUE}
pred <- predict(rFraw, test_raw[,7:58])
pred
```

[01]: http://groupware.les.inf.puc-rio.br/har
